---
title: "Assignment: Building an R Package (fars functions)"
author: "Leo Franco"
date: "26 Feb 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Assignment: Building an R Package (fars functions)}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Building an R Package

The idea of this assignment is to learn to build a package. The content
of it is not really important so I don't know what to add in the vignette.

What I would like to see in a vignette is a short description of the package
and how to use it.

##  Fatality Analysis Reporting System

There are three main functions you can use, see xamples below:

## The function *fars_map_state* plots the occurences in a state in agiven year:
```{r}
library(fars)
library(maps)
library(magrittr)
fars_map_state("21",2014)
```

## The function *fars_summarize_years* gives a summary of accidents for a vector of years:
```{r}
fars_summarize_years(c(2014,2015))
```

## The function *fars_read_years* creates a tibble by reading each file per year:
```{r}
fars_read_years(c(2014,2015))
```

